### 2016-08-02 main.tex
Add a reference that Sam Sober mentioned in his review--a nice application.

This consistency allows a variety of experiments if precise moments in
song can reliably be detected quickly enough to trigger other
apparatus during singing.  A common area of study with this
song-triggering technique is the anterior forebrain pathway (AFP), a
homologue of mammalian basal ganglia consisting of a few distinct
brain areas concerned with the acquisition and learning of song.  For
example, \cite{Kao2005} stimulated the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song and showed that this area
repeatably controls specific variables in song output.
\cite{Wang2008interhemispheric} stimulated LMAN and the high vocal
centre (HVC) in one hemisphere or the other, and found that control of
song rapidly switches between hemispheres.  \cite{Keller2009}
investigated the response of cells in field L and the caudolateral
mesopallium during song with and without feedback perturbations as
well as external sounds, and concluded that these regions may hold a
representation of song against which auditory signals are compared.
\cite{Tumer2007pitchshift} played a disruptive sound during renditions of a syllable that were
slightly above (or below) its average pitch, and showed that the
presence of this apparently random natural variability in songbird
motor output is used to drive change in the song.  \cite{Andalman2009}
extended this experiment and showed that AFP produces a corrective
signal to bias song away from those disruptions.  \cite{Warren2011}
showed that that AFP transfers this signal to the robust nucleus of
the arcopallium (RA) using NMDA-receptor--mediated glutamatergic
transmission. By looking at song recovery after applying the same
pitch-shift paradigm, \cite{Canopoli2014} showed that the caudal
medial nidopallium is implicated in memorising or recalling a recent
song target, but for neither auditory processing nor directed motor
learning.

@@

A variety of syllable-triggering systems have been used, but few have
been documented or characterised in detail.  In 1999,
\cite{Leonardo1999} used groups of IIR filters with hand-tuned logical
operators.  Their system had a latency of 50 or 100 milliseconds (ms),
and they do not report on jitter or accuracy.  As access to
computational resources has improved, approaches have changed: in
2009, \cite{Andalman2009} still used hand-tuned filters, but ran them
on a Tucker-Davis Technologies digital signal processor.  They report
a latency of around 4 ms, but as with other filter-bank techniques, it
is not strictly a syllable detector but rather a pitch and timbre
detector---it cannot identify a frequency sweep, or distinguish a
short chirp from a long one---and thus requires careful selection of
target syllables.  Furthermore, the method is neither inexpensive nor,
based on our experience with a similar technique, accurate.
\cite{Keller2009} applied a neural network to a spectral image of
song.  They report a jitter of 4.3 ms, but further implementation and
performance details are not available.  In 2011, \cite{Warren2011}
matched spectral templates to stable portions of syllables in 8-ms
segments.  They report a jitter of 4.5 ms, and false-negative and
false-positive rates of up to 2\% and 4\%, respectively.  Hardware
requirements and ease of use were not reported.  In 2013,
\cite{Skocik2013} described in detail a system that matches spectral
images of template syllables using a correlation coefficient.  With a
fast desktop (Intel i7 six-core) running Linux and equipped with a
National Instruments data acquisition card, it boasts a hardware-only
(not accounting for the time taken to compute a match with a syllable)
latency and jitter of just a few microseconds, and the detection
computation they use should not much increase that.  Drawbacks are
that some hand-tuning may still be required, and that they report
false-negative rates around 4\% and 7\% for zebra finches and
Bengalese finches respectively, measured on a small dataset.  In much
other work, an allusion is made to a syllable detector, but no further
information is provided.

@@

We evaluate the time taken from the presentation of each instance of
the target syllable to the firing of the detector's TTL pulse---for
example, if the target trigger point with respect to the aligned songs
is at 200 ms, and for a given presentation of the song the detector
fires at 203 ms, we take the latency on that trial to be 3 ms.

@@

    %\bibliography{birds}
\begin{thebibliography}{10}

\bibitem{Kao2005}
Kao MH, Doupe AJ, Brainard MS.
\newblock Contributions of an avian basal ganglia--forebrain circuit to
  real-time modulation of song.
\newblock Letters to Nature. 2005 February;433:638--643.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v433/n7026/abs/nature03127.html}.

\bibitem{Wang2008interhemispheric}
Wang CZH, Herbst JA, Keller GB, Hahnloser RHR.
\newblock Rapid Interhemispheric Switching during Vocal Production in a
  Songbird.
\newblock PLOS Biology. 2008 October;6(10).
\newblock Available from:
  \url{http://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.0060250}.

\bibitem{Keller2009}
Keller GB, Hahnloser RHR.
\newblock Neural processing of auditory feedback during vocal practice in a
  songbird.
\newblock Nature. 2009 January;457:187--190.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v457/n7226/abs/nature07467.html}.

\bibitem{Tumer2007pitchshift}
Tumer EC, Brainard MS.
\newblock Performance variability enables adaptive plasticity of 'crystallized'
  adult birdsong.
\newblock Nature. 2007 December;450:1240--1244.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v450/n7173/abs/nature06390.html}.

\bibitem{Andalman2009}
Andalman AS, Fee MS.
\newblock A basal ganglia-forebrain circuit in the songbird biases motor output
  to avoid vocal errors.
\newblock Proceedings of the National Academy of Sciences of the United States
  of America. 2009 July;106(30):12518--12523.
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2709669/}.

\bibitem{Warren2011}
Warren TL, Tumer EC, Charlesworth JD, Brainard MS.
\newblock Mechanisms and time course of vocal learning and consolidation in the
  adult songbird.
\newblock Journal of Neurophysiology. 2011 October;106(4):1806--1821.
\newblock Available from:
  \url{http://jn.physiology.org/content/106/4/1806.full}.

\bibitem{Canopoli2014}
Canopoli A, Herbst JA, Hahnloser RHR.
\newblock A Higher Sensory Brain Region Is Involved in Reversing
  Reinforcement-Induced Vocal Changes in a Songbird.
\newblock The Journal of Neuroscience. 2014;34(20):7018--7026.
\newblock Available from:
  \url{http://www.jneurosci.org/content/34/20/7018.full}.

\bibitem{Leonardo1999}
Leonardo A, Konishi M.
\newblock Decrystallization of adult birdsong by perturbation of auditory
  feedback.
\newblock Nature. 1999 June;399:466--470.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v399/n6735/abs/399466a0.html}.

\bibitem{Skocik2013}
Skocik M, Kozhevnikov A.
\newblock Real-time system for studies of the effects of acoustic feedback on
  animal vocalizations.
\newblock Frontiers in Neural Circuits. 2013 January;6(111).
\newblock Available from:
  \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3539774/}.

\bibitem{Poole2012}
Poole B, Markowitz JE, Gardner TJ.
\newblock The Song Must Go On: Resilience of the Songbird Vocal Motor Pathway.
\newblock PLOS One. 2012 June;7(6).
\newblock Available from:
  \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038173}.

\bibitem{Jacobsen2003SlidingDFT}
Jacobsen E, Lyons R.
\newblock The sliding DFT.
\newblock IEEE Signal Processing Magazine. 2003 Mar;20(2):74--80.
\newblock Available from:
  \url{http://www.cmlab.csie.ntu.edu.tw/DSPCourse/reference/Sliding\%20DFT.pdf}.

\bibitem{hkp}
Hertz JA, Krogh AS, Palmer RG.
\newblock Introduction to the Theory of Neural Computation.
\newblock Perseus Books; 1991.

\bibitem{Markowitz:2015ko}
Markowitz JE, Liberti WA, Guitchounts G, Velho T, Lois C, Gardner TJ.
\newblock Mesoscopic Patterns of Neural Activity Support Songbird Cortical
  Sequences.
\newblock PLOS Biology. 2015 June;13(6):e1002158--20.
\newblock Available from:
  \url{http://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.1002158}.

\bibitem{Adelsberger:2005dy}
Adelsberger H, Garaschuk O, Konnerth A.
\newblock {Cortical calcium waves in resting newborn mice.}
\newblock Nature Neuroscience. 2005 August;8(8):988--990.
\newblock Available from:
  \url{http://www.nature.com/neuro/journal/v8/n8/full/nn1502.html}.

\bibitem{Schulz:2012fv}
Schulz K, Sydekum E, Krueppel R, Engelbrecht CJ, Schlegel F, Schr{\"o}ter A,
  et~al.
\newblock {Simultaneous BOLD fMRI and fiber-optic calcium recording in rat
  neocortex}.
\newblock Nature Methods. 2012 May;9(6):597--602.
\newblock Available from:
  \url{http://www.nature.com/nmeth/journal/v9/n6/full/nmeth.2013.html}.

\bibitem{Cui:2013dq}
Cui G, Jun SB, Jin X, Pham MD, Vogel SS, Lovinger DM, et~al.
\newblock {Concurrent activation of striatal direct and indirect pathways
  during action initiation}.
\newblock Nature. 2013 February;494(7436):238--242.
\newblock Available from:
  \url{http://www.nature.com/nature/journal/v494/n7436/full/nature11846.html}.

\bibitem{Adelsberger:2014jd}
Adelsberger H, Zainos A, Alvarez M, Romo R, Konnerth A.
\newblock {Local domains of motor cortical activity revealed by fiber-optic
  calcium recordings in behaving nonhuman primates.}
\newblock Proceedings of the National Academy of Sciences of the United States
  of America. 2014 January;111(1):463--468.
\newblock Available from: \url{http://www.pnas.org/content/111/1/463.full}.

\bibitem{Gunaydin:2014dh}
Gunaydin LA, Grosenick L, Finkelstein JC, Kauvar IV, Fenno LE, Adhikari A,
  et~al.
\newblock {Natural neural projection dynamics underlying social behavior.}
\newblock Cell. 2014 June;157(7):1535--1551.
\newblock Available from:
  \url{http://www.cell.com/cell/fulltext/S0092-8674%2814%2900659-X}.

\bibitem{MandelblatCerf:2014eu}
Mandelblat-Cerf Y, Las L, Denissenko N, Fee M.
\newblock {A role for descending auditory cortical projections in songbird
  vocal learning}.
\newblock Elife. 2014 January;3(0):e02152--e02152.
\newblock Available from: \url{https://elifesciences.org/content/3/e02152}.

\bibitem{Noll1970pitchdetection}
Noll AM.
\newblock Pitch determination of human speech by the harmonic product spectrum,
  the harmonic sum spectrum, and a maximum likelihood estimate.
\newblock In: Proceedings of the symposium on computer processing in
  communications. vol.~19; 1970. p. 779--797.

\end{thebibliography}

>>>>

This consistency allows a variety of experiments if precise moments in
song can reliably be detected quickly enough to trigger other
apparatus during singing.  A common area of study with this
song-triggering technique is the anterior forebrain pathway (AFP), a
homologue of mammalian basal ganglia consisting of a few distinct
brain areas concerned with the acquisition and learning of song.  For
example, \cite{Kao2005} stimulated the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song and showed that this area
repeatably controls specific variables in song output.
\cite{Wang2008interhemispheric} stimulated LMAN and the high vocal
centre (HVC) in one hemisphere or the other, and found that control of
song rapidly switches between hemispheres.  \cite{Keller2009}
investigated the response of cells in field L and the caudolateral
mesopallium during song with and without feedback perturbations as
well as external sounds, and concluded that these regions may hold a
representation of song against which auditory signals are compared.
\cite{Tumer2007pitchshift} played a disruptive sound during renditions
of a syllable that were slightly above (or below) its average pitch,
and showed that the presence of this apparently random natural
variability in songbird motor output is used to drive change in the
song.  \cite{Andalman2009} extended this experiment and showed that
AFP produces a corrective signal to bias song away from those
disruptions.  \cite{Charlesworth2011learning} showed that the song
change was isolated to within roughly 10 milliseconds (ms) of the
stimulus, and further proposed an elegant model that predicts the
shape of the learned response and suggests a simple mechanism.
\cite{Warren2011} showed that that AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission. By looking at song
recovery after applying the same pitch-shift paradigm,
\cite{Canopoli2014} showed that the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning.

@@

A variety of syllable-triggering systems have been used, but few have
been documented or characterised in detail.  In 1999,
\cite{Leonardo1999} used groups of IIR filters with hand-tuned logical
operators.  Their system had a latency of 50 or 100 ms,
and they do not report on jitter or accuracy.  As access to
computational resources has improved, approaches have changed: in
2009, \cite{Andalman2009} still used hand-tuned filters, but ran them
on a Tucker-Davis Technologies digital signal processor.  They report
a latency of around 4 ms, but as with other filter-bank techniques, it
is not strictly a syllable detector but rather a pitch and timbre
detector---it cannot identify a frequency sweep, or distinguish a
short chirp from a long one---and thus requires careful selection of
target syllables.  Furthermore, the method is neither inexpensive nor,
based on our experience with a similar technique, accurate.
\cite{Keller2009} applied a neural network to a spectral image of
song.  They report a jitter of 4.3 ms, but further implementation and
performance details are not available.  In 2011, \cite{Warren2011}
matched spectral templates to stable portions of syllables in 8-ms
segments.  They report a jitter of 4.5 ms, and false-negative and
false-positive rates of up to 2\% and 4\%, respectively.  Hardware
requirements and ease of use were not reported.  In 2013,
\cite{Skocik2013} described in detail a system that matches spectral
images of template syllables using a correlation coefficient.  With a
fast desktop (Intel i7 six-core) running Linux and equipped with a
National Instruments data acquisition card, it boasts a hardware-only
(not accounting for the time taken to compute a match with a syllable)
latency and jitter of just a few microseconds, and the detection
computation they use should not much increase that.  Drawbacks are
that some hand-tuning may still be required, and that they report
false-negative rates around 4\% and 7\% for zebra finches and
Bengalese finches respectively, measured on a small dataset.  In much
other work, an allusion is made to a syllable detector, but no further
information is provided.

@@

We evaluate the time taken from the presentation of each instance of
the target syllable to the firing of the detector's TTL pulse---for
example, if the target trigger point is at 200 ms with respect to the
corpus of aligned songs, and for a given presentation of the song the
detector fires at 203 ms, we take the latency on that trial to be 3
ms.

@@

    %\bibliography{birds}
\bibliography{birds}
